Gravitational wave sources in our Galactic backyard: Predictions for BH and NS binaries in LISA

### 2021-06-20 paper/tex/sections/discussion.tex
justify calling it simpler a bit better

\subsection{Assessing the impact of Milky Way model choices}
In this section, we repeat our main analysis but instead apply a simpler model for the Milky Way in order to assess the effect of using a metallicity-dependent Milky Way model. For this purpose, we use model for the Milky Way used in \citet{Breivik+2020} as this is representative of the models used in most previous works.

@@

We show this model in Fig.~\ref{fig:simple_mw} in the same form as Fig.~\ref{fig:galaxy_schematic} for ease of comparison between our models. The two main differences we can see in these plots are that the \citet{Breivik+2020} model is more centrally concentrated and only has two fixed metallicity populations. In addition, though it can't be seen in these plots, the simpler prescriptions for the star formation histories mean that the overall star formation history is highly discontinuous at $\tau = 9 \unit{Gyr}$ and significantly more star formation occurs from $\tau = 9 \unit{Gyr}$ to $\tau = 11 \unit{Gyr}$.

\begin{figure}[ht]
    \centering
    \includegraphics[width=\columnwidth]{../figures/random_simple_galaxy.png}
    \caption{As Fig.~\ref{fig:galaxy_schematic} (right panel), but for the Milky Way model used in \citet{Breivik+2020}.}
    \label{fig:simple_mw}
\end{figure}

>>>>

\subsection{Assessing the impact of Milky Way model choices}
The model that we use for the Milky Way adds several layers of complexity, accounting for the inside-out growth of the thin disc, using empirically informed star formation histories that are a function of time and assigning metallicities based on the position and age of binaries. In this section, we repeat our main analysis but instead apply a simpler model for the Milky Way in order to assess the effect of these added features. For this purpose, we use model for the Milky Way used in \citet{Breivik+2020} as this is representative of the models used in most previous works.

@@

We show this model in Fig.~\ref{fig:simple_mw} in the same form as Fig.~\ref{fig:galaxy_schematic} for ease of comparison between our models. The two main differences we can see in these plots are that the \citet{Breivik+2020} model is more centrally concentrated and only has two fixed metallicity populations.
% leaving this out for now as it didn't come up later
%In addition, though it can't be seen in these plots, the simpler prescriptions for the star formation histories mean that the overall star formation history is highly discontinuous at $\tau = 9 \unit{Gyr}$ and significantly more star formation occurs from $\tau = 9 \unit{Gyr}$ to $\tau = 11 \unit{Gyr}$.

\begin{figure}[t]
    \centering
    \includegraphics[width=\columnwidth]{../figures/random_simple_galaxy.png}
    \caption{As Fig.~\ref{fig:galaxy_schematic} (right panel), but for the Milky Way model used in \citet{Breivik+2020}.}
    \label{fig:simple_mw}
\end{figure}
